%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ivv_inspect.tex
% Inspections of the Simulation Interface Model
%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\inspection{Top-level Inspection}
\label{inspect:TLI}
This document structure, the code, and associated files have been inspected.
With the exception of the cyclomatic complexity of the
\verb|JeodTrickMemoryInterface::primitive attributes| method,
the \ModelDesc satisfies requirement~\traceref{reqt:toplevel}.
A waiver has been granted for this one exception.

\inspection{Design Inspection}
\label{inspect:design}
%\tracingall
Table~\ref{tab:design_inspection} summarizes the key elements of the
implementation of the \ModelDesc that satisfy requirements levied on the model.
By inspection, the \ModelDesc satisfies
requirements~\tracerefrange{reqt:hidden_data_visibility}{reqt:extensibility}.

\begin{longtable}%
  {||l @{\hspace{4pt}} %
   >{\raggedright\arraybackslash}p{1.38in} |%
   >{\raggedright\arraybackslash}p{3.95in}|}
\caption{Design Inspection}
\label{tab:design_inspection} \\[6pt]
\hline
\multicolumn{2}{||l|}{\bf Requirement} & \bf{Satisfaction}
\\ \hline\hline
\endfirsthead

\caption[]{Design Inspection (continued from previous page)} \\[6pt]
\hline
\multicolumn{2}{||l|}{\bf Requirement} & \bf{Satisfaction}
\\ \hline\hline
\endhead

\hline \multicolumn{3}{r}{{Continued on next page}} \\
\endfoot

\hline
\endlastfoot

\ref{reqt:hidden_data_visibility} & Hidden Data Visibility &
  The macro \verb|JEOD_MAKE_SIM_INTERFACES| provides the required
  simulation engine agnostic capability. The implementation of this macro
  is simulation engine specific. Trick-specific implementations make
  protected and private data visible to Trick.
\tabularnewline[4pt]

\ref{reqt:allocated_data_visibility} & Allocated Data Visibility &
  The member functions
  \verb|register_allocation| and \verb|deregister_allocation|
  in the abstract class \verb|JeodTrickMemoryInterface|
  specify the simulation engine agnostic capability. The implementations
  of these methods in the class \verb|JeodTrickMemoryInterface|
  make allocated data visible to Trick.
\tabularnewline[4pt]

\ref{reqt:sim_engine_interface} & Simulation Engine Interface &
  The only Trick dependencies outside of the \ModelDesc are the
  noted exception in the \DYNMANAGER. All other simulation engine
  interfaces are encapsulated within the \ModelDesc.
\tabularnewline[4pt]

\ref{reqt:integ_interface} & Integration Interface &
  The abstract class \verb|IntegratorInterface| provides the required
  simulation engine agnostic capabilities. Trick-specific
  classes that derive from this abstract class provide implementations
  of the required functionality in both the Trick 7 and Trick 10
  environments.
\tabularnewline[4pt]

\ref{reqt:job_cycle} & Job Cycle &
  The function \verb|JeodSimulationInterface::get_job_cycle|
  is the public interface to this required functionality.
  This invokes the pure virtual protected member function
  \verb|get_job_cycle_internal|.
  The class \verb|BasicJeodTrickSimInterface| implements this
  function in the context of a Trick-based simulation.
\tabularnewline[4pt]

\ref{reqt:trick_message_handler} & Trick Message Handler &
  The \ModelDesc provides the class \verb|TrickMessageHandler|, which
  derives from the class \verb|SuppressedCodeMessageHandler|
  and which implements the functionality required of a \verb|MessageHandler|
  using Trick's messaging system.
\tabularnewline[4pt]

\ref{reqt:checkpoint_restart} & Checkpoint/Restart &
  The \ModelDesc provides a generic checkpoint/restart capability in the
  form of classes that create and read from a sectioned checkpoint file.
  The class \verb|JeodTrick10MemoryInterface| uses these
  generic capabilities to provide the required ability to make
  JEOD-based simulations checkpointable and restartable in a
  Trick 10 environment.
\tabularnewline[4pt]

\ref{reqt:addr_name_xlate} & Address/Name Translation &
  The functions \verb|get_name_at_address| and \verb|get_address_at_name|
  in the classes \verb|JeodSimulationInterface| (static) and
  \verb|JeodMemoryInterface| (pure virtual)
  are the public interfaces to this required functionality.
  The class \verb|JeodTrickMemoryInterface| provides dummy
  implementations while \verb|JeodTrick10MemoryInterface| provides
  functional implementations of these functions.
\tabularnewline[4pt]

\ref{reqt:multiple_integ_groups} & Multiple Integration Groups &
  The \ModelDesc implements this requirement as a set of JEOD-agnostic
  classes (which may eventually be migrated out of JEOD) and the JEOD-aware
  class \verb|JeodDynbodyIntegrationLoop|.
\tabularnewline[4pt]

\ref{reqt:extensibility} & Extensibility &
  The \ModelDesc was carefully designed to have the public interfaces be in
  the form generic macros and abstract, simulation engine agnostic classes.
  The Trick independent demonstration and the test harness
  used in the JEOD unit tests illustrate to some extent
  that the model can be extended for use outside of the Trick environment.
\tabularnewline[4pt]

\end{longtable}