\chapter{User Guide}\hyperdef{part}{user}{}\label{ch:user}
%----------------------------------
The User Guide is divided into three instruction sets:
\begin{enumerate}
 \item \textbf{Instructions for Simulation Users}.  This instruction-set
 contains a description of how to modify \ModelDesc\ variables after the
 simulation has compiled, including an in-depth discussion of the input file;
 an overview of how to interpret (but not edit) the S\_define file; and a
 sample of some of the typical variables that may be logged.
 \item \textbf{Instructions for Simulation Developers}.  This instruction-set
 builds on the previous set, and adds information on the necessary
 configuration of the \ModelDesc\ within an S\_define file, and the creation of
 standard run directories.
 \item \textbf{Instructions for Model Developers}.   This instruction-set
 builds on the previous set, and adds information on the potential for
 extending the model to perform tasks that are beyond its current abilities.
\end{enumerate}

\section{Instructions for Simulation Users}\label{sec:guide_sim_user}
\input{guide_simuser}
\section{Instructions for Simulation Developers}
\input{guide_simdev}
\section{Instructions for Model Developers}

The \ModelDesc is intended to provide a baseline configuration for objects that
have mass.  It is quite extensible.

Authors of an extension will have to pay close attention to the limitations of
the \ModelDesc, and consider whether the methods provided are suitable for the
task in the new environment.  For example, when attaching two bodies, the
\ModelDesc provides all of the functionality associated with positioning the
mass bodies correctly in the mass tree, with the correct orientation and
relative positions.  It does not provide any capabilities for modeling the
changes to the dynamic state, because it knows nothing of any dynamic states.