\chapter{Product Specification}\hyperdef{part}{spec}{}\label{ch:spec}
%----------------------------------

\section{Conceptual Design}
\input{spec_concept}


\section{Mathematical Formulations}
\input{spec_math}

\section{Detailed Design}\label{sec:detailed_design}
\subsection{API}
Follow this link for the 
\href{file:refman.pdf}{\em \ModelDesc\ API}~\cite{api:mass}.

\subsection{Class Overview}

The MassBody is the basic class for a Mass Body.  It comtains (this is not an 
exhaustive list):
\begin{itemize}
 \item \textit{core\_properties}, an instance of MassProperties, that 
 describes the properties of the MassBody as a single entity.
 \begin{itemize}
  \item A MassProperties class is a MassBasicPoint which also provides data 
  elements for mass and the inertia tensor.
  \begin{itemize}
   \item A MassBasicPoint is a MassPointState that provides the linkages 
   within the mass tree (to its children, parent, etc.).  A mass tree 
   comprises the collection of MassBasicPoint instances that are physically 
   connected at some point.
   \begin{itemize}
    \item A MassPointState provides data elements for the position of the 
    point, and the orientation of the axes associated with the point, with 
    respect to some parent.
   \end{itemize}
   \item A related item, a MassPoint, is simply a MassBasicPoint with a name, 
   allowing for it to be found easily.
  \end{itemize}
  \end{itemize}
 

 \item \textit{composite\_properties}, another instance of MassProperties, 
 that describes the properties of the subtree of which the body is the head.
 \item \textit{structure\_point}, an instance of MassBasicPoint (see above).
\end{itemize}

Note that since a MassProperties is a MassBasicPoint, it must have a parent 
for evaluation of its position and orientation.  The parent of both instances 
of Mass Properties (\textit{core\_properties} and 
\textit{composite\_properties}) is the MassBasicPoint  
\textit{structure\_point}; the position and orientation are stated relative to 
the structural axes.


\subsection{Attaching Bodies}\label{sec:attaching_bodies}
Attaching two bodies together is typically performed with a Body Action.  A 
rough outline of the algorithm is presented here, instructions for 
implementation are contained in the Body Action document 
(\cite{dynenv:DYNBODY}).

The following rules provide the restrictions on which bodies can be commanded 
attached to which bodies.
\begin{itemize}
 \item A DynBody (extension of MassBody) can never be a child of a basic 
 MassBody.
 \item There can be no circular attachments.
\end{itemize}
IMPORTANT NOTE: Only root bodies may actually attach to another body.  While 
it may be legal to command the attachment of body A to body B (subject to the 
rules above), the attachment in the mass tree will be represented as the root 
of the tree containing body A attaching to body B.

\subsubsection{Attaching using Points}
The easiest implementation of attaching two bodies is to define an attach 
point (a MassPoint) on each body, and make those points coincident, with their 
z-axes aligned, and their x- and y-axes both anti-aligned.  Because each 
MassPoint will have position and orientation defined with respect to its 
respective body's structural axes, it is a striaghtforward undertaking to 
obtain the orientation and position of the child body's structural axes with 
respect to the parent body's structural axes.  Then, the general attachment 
method can be implemented, and the parent will have as children its MassPoint 
used for attachment and the child structure-point; the child will have as a 
child its MassPoint used for attachment.

\subsubsection{Attaching using Offset and Orientation}
This more general form of the attach process requires knowledge of the 
orientation and relative position of the child body's structural-axes with 
respect to those of the parent body, which may be provided directly or from 
the previous method.  

If the child body is not the root of its own tree, its root is first found, 
then the relative position and orientation of that root body's structure-axes 
relative to the structure-axes of the parent body are determined.

With the root state known, the attachment of the root of the child's tree (the 
child-root) to the parent can proceed in three steps:
\begin{enumerate}
\item{\bf Validate:} Is this a valid attachment which for the \ModelDesc, 
means it follows a tree structure and avoids 
invalid circular attachments.
\item{\bf Establish Links:} The child-root MassBody is required to establish 
the links to the parent MassBody that define their 
relationship in the mass tree.
\item{\bf Update Properties:}  The parent MassBody updates its composite 
properties to reflect the addition of the child-root MassBody.  
The composite properties of the child-root remain unchanged.
\end{enumerate}
 
A few examples will help illustrate the concept of attachments and we will 
start by supposing that we have three MassBodys called 
A, B, and C respectively.

In the first example we decide to attach MassBody C to MassBody B thereby 
making C a child of B.  Given that no other attachments exist in
this example this is a valid attachment so we will pass step one(Validate).  
In step two(Establish Links) the child will update the 
links between the two MassBodys including MassPointLinks and MassBodyLinks.  
In step three(Update Properties) the parent will 
update its composite properties (mass, inertia, center of mass) to represent 
the combined state.

Building on the new mass tree created with the attachment of MassBody C to 
MassBody B, we will now attach MassBody B to MassBody A. 
MassBody B will then become a child of MassBody A, and MassBody C will remain 
a child of MassBody B.  In this attachment process, the validity is checked -- 
since A is not already attached to B or C this is approved.  MassBody B now 
performs the Establish Links step configuring all MassPointLinks and 
MassBodyLinks with MassBody A.  Then MassBody A uses the composite properties 
of MassBody B to perform the Update Properties step.  It should be noted that 
the
composite properties of MassBody B already include the properties of
MassBody C so, following the update, the composite properties of A represent 
the entire tree.
Even though the properties of A do contain information for the entire tree, 
MassBody A has no knowledge that
MassBody C exists.  MassBody A only knows about MassBody B.

Consider another situation: return to the situation where only MassBody B and 
MassBody C are attached and C is a child of B.  
Suppose we then want to attach MassBody C to MassBody A.  The \ModelDesc\ 
recognizes that MassBody C is not a root body, so instead attaches MassBody B 
to MassBody A.  The offset and rotation of B with respect to A are set such 
that the offset and rotation of C with respect to A are as requested.  Again,
the composite mass properties of A will include those of C through the 
composite properties of B.

In both situations, the mass tree looks identical.

\subsection{Detach Overview}
In the detach scenario, the links between the body to be detached and its 
parent are severed, and the composite properties of the parent are updated to 
reflect that one of its children has been removed.  The composite properties 
of the child body are unchanged.
\clearpage
\boilerplateinventory
