

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Purpose:  Detailed part of Product Spec for the time model
%
% 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Detailed Design}

This section is divided into 4 parts:


\begin{itemize}
\item A process flow-through description (Process Architecture)
of the sequence in which the
various functions are called, and the interaction between the objects.
\item A complete list and description of all methods that comprise the
\timeDesc.
\item A description of the external data files used by the objects.
\item A description of the extension capability of the model.
\end{itemize}

Further, the
\href{file:refman.pdf} {\em Reference Manual} \cite{timebib:ReferenceManual}
contains a
structural overview of the \timeDesc.



\input{timeSpec_Detailed_Proc}
\clearpage
\input{timeSpec_Detailed_Func}


\clearpage

\subsection{Default data files}
This section describes the data files included with the release
of \JEODid.

{\begin{enumerate}
\funcitem{tai\_to\_ut1.cc}
This file gives a tabulation of the differences between \textit{TAI} and
\textit{UT1} as a function of \textit{TAI}.

Instructions for updating this file are contained in the Extension
section of the User Guide (chapter \ref{ch:user}).

\funcitem{tai\_to\_utc.cc}
This file gives a tabulation of the differences between \textit{TAI} and
\textit{UTC} as a function of \textit{UTC}.

Instructions for updating this file are contained in the Extension
section of the User Guide (chapter \ref{ch:user}).

\end{enumerate}}



\clearpage
\subsection{Extensibility}
The Time Representations Model is designed in such a way that it can
easily be extended with the addition of more time representations.

Each new time representation must meet the following requirements:


\begin{enumerate}
\item It shall be included as a class of its own, inheriting from JeodBaseTime
or TimeStandard.
\item It shall have a name
\item It shall have a constructor and destructor
\item There shall be some method for deriving its value from one of the
time classes that already exist.
\end{enumerate}



A new time representation must have a new Time Converter.  A user may
also wish to define a new Time Converter to convert directly between two
preexisting time representations (e.g., UT1 to MET).

Each new Time Converter must meet the following requirements:

\begin{enumerate}
	\item A converter shall be defined to allow the derivation of the new
	time representations.
	\item The converter shall be included in a class of its own, inheriting
	from \textit{TimeConverter}.
	\item The converter class shall define one or both of the methods
\begin{enumerate}
	\item \textit{convert\_a\_to\_b}.
  \item \textit{convert\_b\_to\_a}.
\end{enumerate}
  \item The converter class shall define the \textit{valid\_directions} attribute to specify when \textit{convert\_a\_to\_b} and/or \textit{convert\_b\_to\_a} is valid.
  \item The converter class shall have an \textit{initialize} method.
  \item The converter class shall have a constructor and a destructor.
\end{enumerate}

Instructions for adding these methods are found in the Extension section
\vref{sec:User_Extension} of the User Guide.
