\setcounter{chapter}{0}

%----------------------------------
\chapter{Introduction}\hyperdef{part}{intro}{}\label{ch:intro}
%----------------------------------

\section{Model Description}
%%% Incorporate the intro paragraph that used to begin this Chapter here.
%%% This is location of the true introduction where you explain why this 
%%% model exists.
%%% Identify the Model context within JEOD.

% The JEOD \SpiceDesc\ ...
\input {spiceIntro}


\section{Document History}
%%% Status of this and only this document.  Any date should be relevant to when 
%%% this document was last updated and mention the reason (release, bug fix, etc.)
%%% Mention previous history aka JEOD 1.4-5 heritage in this section.
%%% Mention that JEOD.pdf is the parent document.

\begin{tabular}{||l|l|l|l|} \hline
\DocumentChangeHistory
\end{tabular}

\section{Document Organization}
This document is formatted in accordance with the 
NASA Software Engineering Requirements Standard~\cite{NASA:SWE} 
and is organized into the following chapters:

\begin{description}
%% longer chapter descriptions, more information.

\item[Chapter 1: Introduction] - 
This introduction contains three sections: description of model, document history, and organization.  
The first section provides the introduction to the \SpiceDesc\ and its reason 
for existence.  It also contains a brief description of the interconnections with other models, and 
references to any supporting documents.  The second section displays the history of this document which includes
author, date, and reason for each revision; it also lists the document that is parent to this one.  The final
section contains a description of the how the document is organized.

\item[Chapter 2: Product Requirements] - 
Describes requirements for the \SpiceDesc.

\item[Chapter 3: Product Specification] - 
Describes the underlying theory, architecture, and design of the \SpiceDesc\ in detail.  It is organized into
three sections: Conceptual Design, Mathematical Formulations, and Detailed Design.

\item[Chapter 4: User Guide] - 
Describes how to use the \SpiceDesc\ in a Trick simulation.  It contains information that will be useful to
both users and developers of simulations. The \SpiceDesc\ is not intended to be extended, so there is no
discussion of how to do so.

\item[Chapter 5: Inspections, Tests, and Metrics] -  
The final chapter describes the procedures and results that demonstrate the satisfaction of the
requirements for the \SpiceDesc.

\end{description}


%----------------------------------
\chapter{Product Requirements}\hyperdef{part}{reqt}{}\label{ch:reqt}
%----------------------------------

\section{Project Requirements}
\requirement{Top-level Requirement}
\label{reqt:toplevel}
\begin{description}
\item[Requirement:]\ \newline
  The \SpiceDesc\ shall meet the JEOD project-wide requirements specified in
  the \JEODid\ Top-Level Document.

\item[Rationale:]\ \newline
  This is a project-wide requirement.

\item[Verification:]\ \newline
  Inspection
\end{description}


\requirement{Solar System Body Ephemeris Representation}
\label{reqt:rep_ephem}
\begin{description}
\item[Requirement:]\ \newline
  The \SpiceDesc\ shall provide the capability to use the JPL SPICE library
  to represent the ephemerides of any solar system body for which a
  corresponding data set is provided.

\item[Rationale:]\ \newline
  The existing JEOD DE4xx model is limited in the number of solar system bodies
  it can represent. SPICE provides a standard way of providing the same bodies,
  as well as virtually any other solar system body desired, so long as the data
  is available for it.

\item[Verification:]\ \newline
  Test
\end{description}


\requirement{Solar System Body Orientation Representation}
\label{reqt:rep_rnp}
\begin{description}
\item[Requirement:]\ \newline
  The \SpiceDesc\ shall provide the capability to use the JPL SPICE library
  to represent the orientation of any solar system body for which a
  corresponding data set is provided.

\item[Rationale:]\ \newline
  Existing JEOD models provide only Earth, Moon, and Mars orientation. SPICE
  provides a standard way of providing these plus many others, so long as the
  data is available for it.

\item[Verification:]\ \newline
  Test
\end{description}


%----------------------------------
\chapter{Product Specification}\hyperdef{part}{spec}{}\label{ch:spec}
%----------------------------------

\section{Conceptual Design}
%The \SpiceDesc\ is ...
\input {spiceConceptual}

\section{Mathematical Formulations}

% The \SpiceDesc\ ...
\input {spiceMathForm}


\section{Detailed Design}

\input {spiceDetail}


%----------------------------------
\chapter{User Guide}\hyperdef{part}{user}{}\label{ch:user}
%----------------------------------

% The \SpiceDesc\ is ...
\input {spiceUserGuide}


%----------------------------------
\chapter{Inspections, Tests, and Metrics}\hyperdef{part}{ivv}{}\label{ch:ivv}
%----------------------------------

% This chapter describes...

\input {spiceVerif}


\newpage
\boilerplatetraceability

\newpage
\boilerplatemetrics
