\chapter{Beeman's Algorithm}\label{app:beeman}

Beeman's algorithm is a two-stage predictor-corrector method.  It requires
knowledge of the velocity-derivative from one integration cycle period before
the start of this integration cycle.  It is, therefore, also a multi-step
method, and requires a primer to launch it.  In JEOD, we use the RK2
integrator as the primer.

Beeman's algorithm explicitly distinguishes generalized position and
generalized velocity. The equations that govern propagation via Beeman's
Algorithm are given by equations~(\ref{eqn:beeman_prime})
to~(\ref{eqn:beeman_1})\cite{beeman:1976}.

Priming (one simulation step):
\begin{equation}
\label{eqn:beeman_prime}
\begin{split}
\dot{\vect v}_{-1} &=
  \dot{\vect v}(t_i-\Delta t, x(t_i-\Delta t),\vect v(t_i-\Delta t)) \\
\end{split}
\end{equation}
Stage 0 (predictor):
\begin{equation}
\label{eqn:beeman_0}
\begin{split}
t_1 &= t_f = t_i + \Delta t \\
\dot{\vect v}_{0} &=
  \dot{\vect v}(t_i, x(t_i),\vect v(t_i)) \\
\bar{\vect v}_1 &= \vect v(t_i) +
   \Delta t
   \left(\frac 2 3 \dot{\vect v}_{0} - \frac 1 6 \dot{\vect v}_{-1}\right) \\
\bar{\dot{\vect x}}_1 &= \dot {\vect x}(\vect x(t_i),\bar{\vect v}_1) \\
\bar{\dot{\vect v}}_1 &=
  \frac 3 2 \dot{\vect v}_{0} - \frac 1 2 \dot{\vect v}_{-1} \\
\vect x(t_1) &= \vect x(t_i) + \Delta t \, \bar{\dot{\vect x}}_1 \\
\vect v(t_1) &= \vect v(t_i) + \Delta t \, \bar{\dot{\vect v}}_1
\end{split}
\end{equation}
Stage 1 (corrector):
\begin{equation}
\label{eqn:beeman_1}
\begin{split}
t_2 &= t_1 = t_f = t_i + \Delta t \\
\dot{\vect v}_{1} &=
  \dot{\vect v}(t_1, x(t_1),\vect v(t_1)) \\
\bar{\dot{\vect v}}_2 &=
  \frac 1 3 \dot{\vect v}_{1} +
  \frac 5 6 \dot{\vect v}_{0} - \frac 1 6 \dot{\vect v}_{-1} \\
\vect x(t_f) &= \vect x(t_1) \\
\vect v(t_f) &= \vect v(t_i) + \Delta t \, \bar{\dot{\vect v}}_2 \\
\dot{\vect v}_{-1} &= \dot{\vect v}_{0}
\end{split}
\end{equation}


Beeman's Algorithm offers significant improvements in accuracy over
the symplectic Euler method. Beeman's algorithm is a second order method
while the Euler methods are first order. Like the fourth-order
Adams-Bashforth-Moulton method, Beeman's Algorithm
is not self-starting. It relies on the derivatives from the previous
time step. JEOD uses the RK2 method as a primer for Beeman's Algorithm.

