\chapter{Product Specification}\hyperdef{part}{spec}{}\label{ch:spec}
Propagating the evolution of a vehicle's translational and/or rotational 
state over the course of a simulation is an essential part of every 
space-based Trick simulation. JEOD assumes a Newtonian universe.
The underlying equations of motion that
describe the changes in state over time are the second order
ordinary differential equations (ODE) given by Newton's second law of motion.
The problem addressed by the \ModelDesc falls into the very broad category of
solving such second order initial value problems.
While analytic solutions do exist for a limited set of such problems,
the complex and unpredictable nature of the forces and torques acting on a
vehicle precludes the use of analytic solutions as a generic solution
to these state propagation problems. Numerical integration techniques
must be used to solve the problem.

Performing this numerical integration is the primary goal of this model.
Several such numerical integration techniques exist. Deciding which technique
is best-suited for the problem at hand is a problem-dependent tradeoff
between accuracy and computational cost. The \ModelDesc thus provides a
variety of numerical integration techniques.

\section{Conceptual Design}
\input{spec_concept}

\section{Key Algorithms}\label{sec:algorithms}
\input{spec_key}

\section{Detailed Design}\label{sec:detailed_design}
\input{spec_detail}

\section {Interactions}
\input{spec_interaction}

\boilerplateinventory
