
\chapter{Product Requirements}\hyperdef{part}{reqt}{}\label{ch:reqt}

\requirement{Project Requirements}
\label{reqt:project}
\begin{description}
\item[Requirement:]\ \newline
  This model shall meet the JEOD project-wide requirements specified in
  the \JEODid\ \hyperTLDinside{part}{reqt}{requirements}.

\item[Rationale:]\ \newline
  This is a project-wide requirement.

\item[Verification:]\ \newline
  Inspection
\end{description}


\requirement{Quaternion Encapsulation}
\label{reqt:encapsulation}
\begin{description}
\item[Requirement:]\ \newline
  The Quaternion model shall encapsulate the data items needed to represent
  a quaternion and the mathematical operations on a quaternion in the form
  of an instantiable class.

\item[Rationale:]\ \newline
  JEOD 2.0 is written in C++. A class is the standard encapsulation
  mechanism used throughout JEOD.
  The overarching purpose of the Quaternion model is to represent
  quaternions as a class.

\item[Verification:]\ \newline
  Inspection
\end{description}


\requirement{Data Representation}
\label{reqt:data}
\begin{description}
\item[Requirement:]\ \newline
  The Quaternion class shall contain the data items needed to
  represent a quaternion as an object.

\item[Rationale:]\ \newline
  Self-evident.

\item[Verification:]\ \newline
  Inspection
\end{description}

\requirement{Represent Orientation}
\label{reqt:orient}
\begin{description}
\item[Requirement:]\ \newline
  The Quaternion class shall provide the mathematical operations needed to
  enable the use of quaternions to represent the orientation of objects  
  and reference frames in three-space.

\item[Rationale:]\ \newline
  The ability to represent orientation of objects and reference frames
  is the key reason for the existence of the Quaternion model.

\item[Verification:]\ \newline
  Inspection, test
\end{description}


\requirement{Conversion}
\label{reqt:conversion}
\begin{description}
\item[Requirement:]\ \newline
  The Quaternion model shall provide means to convert left transformation
  unit quaternions to and from
  \subrequirement{Column vector transformation matrices}
  \label{reqt:xform_convert},
  \subrequirement{eigen rotations}
  \label{reqt:eigen_convert}, and
  \subrequirement{four vectors}
  \label{reqt:fourvec_convert}.

\item[Rationale:]\ \newline
  \begin{itemize}
  \item Conversion to and from transformation matrices is an essential
    capability used by many other JEOD models.
  \item There are many other charts on SO(3). Eigen rotations is one of
    them.
  \item A quaternion needs to be converted to a primitive type to enable
    communication with outside agents and simulations.
  \end{itemize}

\item[Verification:]\ \newline
  Inspection, test
\end{description}
