%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Purpose:
%
% 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

The gravitational forces due to the Earth are modeled on
the basis of a set of constant coefficients and a force
model that computes the accelerations, referred to as a geopotential model.
The current geopotential model available to \JEODid\
Geopotential models are commonly a function of a form of
Earth Centered
Earth Fixed, or ECEF, coordinates.  In order to transform from
an Earth Centered Inertial frame
to the ECEF system a matrix rotation must be made.

These rotations can take many forms. The most common for Earth
is one composed of four individual matrix operations.
These operations account for precession, nutation, polar offset and rotation.
This document will refer to this process as the
\ModelDesc,
or the RNP Model.

The \JEODid\ RNP model has been built as an extensible
software framework. The basis for this framework
is an interface to the JEOD Ephemerides model.
This gives a standard interface for controlling
the orientation between a planet's inertial
frame and its planet fixed frame, regardless of the
formulation for the orientation. Additionally, there
is an implementation of this interface that builds
a framework for implementation planet rotation models
that follow
the previously mentioned RNP paradigm.
This allows for reuse of code, where different
representations of planet RNP can be created while
taking advantage of a common framework. This document describes how this
common framework can be extended for use with any rotation model that
follows the RNP paradigm.

This document also describes two specific implementations of the \JEODid\
\ModelDesc. The basic reference system of \JEODid\ is the inertial coordinate
system known as J2000. The particular representation of RNP that transforms
from the J2000 inertial coordinate system to the ECEF frame, has been
implemented using the \JEODid\ RNP Model, and this document describes the \JEODid\
implementation of the J2000 (FK5) representation of Earth RNP. The document
also describes an implementation of an RNP representation for the planet Mars,
which is new to JEOD as of the version 2.2 release.

Note that while the RNP Model started as a planet orientation model specific to
RNP, it has now expanded to support interfaces for any formulation of planet
orientation. However, the name has stayed the same for legacy and consistency
purposes.

\end{abstract}
