%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MassBodyInit_spec.tex
% Specification of the MassBodyInit class
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Product Specification}\label{ch:\modelpartid:spec}

\section{Conceptual Design}
The MassBodyInit class initializes the subject body's mass
properties and establishes the subject body's mass points.
The class derives directly from the model BodyAction base class.

\section{Mathematical Formulations}
All of the underlying mathematics is performed by the Mass Model.
Refer to the Mathematical Formulations section of
the \hypermodelref{MASS}.

\section{Detailed Design}
This is a very simple sub-model. It adds three data elements to
the base class and overrides the base class {\tt apply()} method.
The data elements are
\begin{description}
\item[properties] type = {\tt MassPropertiesInit} \\
      Specifications for the subject mass body's core mass properties.
\item[points] type = {\tt MassPointInit *} \\
      Specifications for the subject mass body's mass points.
\item[num\_points] type = {\tt unsigned int} \\
      Size of the points array.
\end{description}

The classes MassPropertiesInit and MassPointInit
are part of the Mass Model.
See the \hypermodelref{MASS} for details.

The {\tt apply()} method calls the subject body's {\tt initialize\_mass()}
method, which initializes the body's mass properties given the supplied mass
properties initialization data and establishes the body's auxiliary mass points
given the supplied mass point initialization data.

The MassBody class initializes its mass points by calling the
{\tt add\_mass\_point()} for each supplied mass point.
The DynBody class overrides the {\tt add\_mass\_point()} method.
The effect of the override is to add the point of interest
to the underlying MassBody object's list of MassPoint objects and
to the DynBody object's list of VehiclePoint objects. These vehicle
points can later be used for attaching bodies and initializing body states.
